Unveiling the Optimal Approach for Neural Network-Based Cosmological Parameter Inference through Likelihood Implicit Methods

### 2023-06-25 paper/paper.tex
cropped plot

\section{Experiment}

@@

%--------------------------------------------------------------------
\section{Results}\label{Sec:results}
%--------------------------------------------------------------------
\section{Conclusions}
%--------------------------------------------------------------------
%--------------------------------------------------------------------
\begin{acknowledgements}
This work was granted access to the HPC/AI resources of IDRIS under the allocation 2022-AD011013922 made by GENCI.
\end{acknowledgements}

>>>>

\section{Experiment}\label{Sec:experiment}

@@

%--------------------------------------------------------------------
\section{Results}\label{Sec:results}
\begin{figure*}
    \centering
\includegraphics[width=\textwidth]{figures/contours_posterior_imp_ex_ps.pdf}
    \caption{
Constraints on the $\Lambda$CDM parameter space as found in the LSST Y10 survey setup. The constraints are obtained by applying the $C_{\ell}$ (light blue contours), the full field explicit inference (yellow contours), and the full field implicit inference strategy (violet contours), described in \autoref{Sec:experiment}.
The contours show the $68\%$ and the $95\%$  confidence regions. The dashed white lines define the true parameter values.}
\label{fig:contours_posterior_imp_ex_ps}
\end{figure*}
%--------------------------------------------------------------------
\section{Conclusions}
%--------------------------------------------------------------------
%--------------------------------------------------------------------
\begin{acknowledgements}
This work was granted access to the HPC/AI resources of IDRIS under the allocation 2022-AD011013922 made by GENCI.
\end{acknowledgements}
